---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CandyHapsinatoR2000

<!-- badges: start -->
[![R-CMD-check](https://github.com/mariegiehmoverby/CandyHapsinatoR2000/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mariegiehmoverby/CandyHapsinatoR2000/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of CandyHapsinatoR2000 is to decide what candy to mix.

## Installation

You can install the development version of CandyHapsinatoR2000 from [GitHub](https://github.com/mariegiehmoverby/CandyHapsinatoR2000) with:

```{r, message = FALSE, warning = FALSE, results = 'hide'}
# Install the package
devtools::install_github("mariegiehmoverby/CandyHapsinatoR2000")
```

## Vignette
You can find the vignette for CandyHapsinatoR2000 [HERE](https://github.com/mariegiehmoverby/CandyHapsinatoR2000/tree/master/vignettes)


## Example

This is a basic example which shows you can use the function

```{r, example}
library(CandyHapsinatoR2000)
candy <- hapsinatoR(pricePer100g = 10, snollerMoney = 100, numRows = 8, numCols = 8, handfulSize = "large")
```

The input in `print()` must be a hapsinatoR object.
```{r example print}
print(candy)
```

Summary of the hapsinatoR object will give you a summary of the candy mix.
```{r example summary}
summary(candy)
```

Plotting the hapsinatoR object will give you a visual representation of what candy to mix.
```{r example plot}
plot(candy)
```
