---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is based on `CandyHapsinator2000` version `r packageVersion("CandyHapsinator2000")` which is avaiable on github at [https://github.com/mariegiehmoverby/CandyHapsinatoR2000].

```{r}
library(CandyHapsinatoR2000)
```

# Different handful sizes for hapsinatoR 
The `hapsinatoR` take various arguments. One of them is handful `handfulSize` which is shown below. 

## small handful size
```{r}
small_hapsinator <- hapsinatoR(pricePer100g = 11.95,
                               snollerMoney = 46,
                               numRows = 5,
                               numCols = 20,
                               handfulSize = "small")

summary(small_hapsinator)
plot(small_hapsinator)
```
## medium handful size
```{r}
medium_hapsinator <- hapsinatoR(pricePer100g = 11.95,
           snollerMoney = 46,
           numRows = 5,
           numCols = 20,
           handfulSize = "medium")

summary(medium_hapsinator)
```

## Large handful size
```{r}
large_hapsinator <- hapsinatoR(pricePer100g = 11.95,
           snollerMoney = 46,
           numRows = 5,
           numCols = 20,
           handfulSize = "large")

summary(large_hapsinator)
```


# Friday price for the candy
We all know that 'mix your own candy' prices are low on fridays to accommodate Fridaytamtam on television, so let's see how the `hapsinatoR` handles this. 

```{r}
# hapsinator with 10 kr. per  100g crandy
friday_hapsinator_10 <- hapsinatoR(pricePer100g = 10,
           snollerMoney = 50,
           numRows = 6,
           numCols = 25,
           handfulSize = "small")

summary(friday_hapsinator_10)
```


```{r}
# hapsinator with 8.95 kr. per  100g crandy
friday_hapsinator_8_95 <- hapsinatoR(pricePer100g = 8.95,
           snollerMoney = 50,
           numRows = 6,
           numCols = 25,
           handfulSize = "small")

summary(friday_hapsinator_8_95)
```

# Visualising the output of the `hapsinatoR`

```{r}
plot(medium_hapsinator)
```

```{r}
plot(large_hapsinator)
```


```{r}
plot(friday_hapsinator_10)
```

```{r}
plot(friday_hapsinator_8_95)
```

